A Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}

### 2019-06-07 main.tex
Wrote a paragraph of CSPに関する補足説明.

\begin{verbatim}
        let a = .< fun x -> x + 1 >. in .< .~a 2 >.
\end{verbatim}

evaluates to \verb|.< (fun x -> x + 1) 2 >.|. We can get the result with run.

\begin{verbatim}
        run (let a = .< fun x -> x + 1 >. in .< .~a 2 >.)
\end{verbatim}

is reduced to 3.

>>>>

\begin{verbatim}
        let plusone = .< fun x -> x + 1 >. in .< .~plusone 2 >.
\end{verbatim}
evaluates to \verb|.< (fun x -> x + 1) 2 >.|. We can get the result with run.
\begin{verbatim}
        run (let plusone = .< fun x -> x + 1 >. in .< .~plusone 2 >.)
\end{verbatim}
is reduced to 3.

\subsubsection{CSPに関する補足説明}
Cross-stage Persistence (CSP) is another primitive of multistage programming, which enable us to embed computed values into a code value.
This is an example of CSP.
\begin{verbatim}
        let plusone = fun x -> x + 1 in
        let a = plusone 2 in  .< a >.
\end{verbatim}
This program evaluates to \verb|.< 3 >.| not  \verb|.< plusone 2 >.|.
This is because the variable \verb|a| is introduced into a code fragment using CSP.
Therefore, the variable \verb|a| is embeded after \verb|a| is calculated.
CSP is very important when we write practival programs 
because CSP enables us to use library functions in code fragments.
